\thesistitle

### 2019-07-22 sections/experimentalsetup.tex
Describe common hierarchy

\subsubsection{Common Hierarchy}
The following relations belong to
\todo{TODO}

>>>>

\subsubsection{Common Hierarchy}
Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances. However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design. This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern. A god object is an object that knows too much or does too much.
